### 2015-05-12 whoop.tex
update in main section

\begin{figure}
\begin{tabular}{lp{5.5cm}}
\textbf{Statement form} & \textbf{Notes} \\\hline
$x = e;$ & private assignment, where $x \in \variables{T}$ and $e$ is an expression over $\variables{T}$ \\\hline
$x = f(\overline{e});$ & procedure call, where $x \in \variables{T}$, $\overline{e}$ is a sequence of expressions over $\variables{T}$, $f$ is the name of a procedure in $\procedures{T}$ \\\hline
$s = e;$ & shared write, where $s \in \sharedvars$ and $e$ is an expression over $\variables{T}$ \\\hline
$x = s;$ & shared read,  where $x \in \variables{T}$ and $s \in \sharedvars$ \\\hline
$\mutexlock{m};$   & mutex lock, where $m \in \mutexes$ \\\hline
$\mutexunlock{m};$ & mutex unlock, where $m \in \mutexes$
\end{tabular}
\caption{Forms of statements in our simple programming model}\label{fig:statements}
\end{figure}

@@

\begin{figure}
\begin{tabular}{ll}
\textbf{Original statement} & \textbf{Instrumented statement} \\\hline
$s = e;$ & $\hasbeenwritten{i} = \hasbeenwritten{i} \cup \{ s \};$ \\
         & $\lockset{s}{i} = \lockset{s}{i} \cap \currentlockset{i};$ \\\hline
$x = s;$ & $\hasbeenread{i} = \hasbeenread{i} \cup \{ s \};$ \\
         & $\lockset{s}{i} = \lockset{s}{i} \cap \currentlockset{i};$ \\
         & $\havoc{\instrument{x}{i}};$ \\\hline
$\mutexlock{m};$   & $\currentlockset{i} = \currentlockset{i} \cup \{ m \};$ \\\hline
$\mutexunlock{m};$ & $\currentlockset{i} = \currentlockset{i} \setminus \{ m \};$ \\\hline
\end{tabular}
\caption{Instrumenting statements for static lockset analysis}\label{fig:instrumentation}
\end{figure}

>>>>

\begin{figure}
\begin{tabular}{lp{5.5cm}}
\textbf{Statement Form} & \textbf{Notes} \\
\toprule

$x = e;$ & private assignment, where $x \in \variables{T}$ and $e$ is an expression over $\variables{T}$ \\
\midrule

$x = f(\overline{e});$ & procedure call, where $x \in \variables{T}$, $\overline{e}$ is a sequence of expressions over $\variables{T}$, $f$ is the name of a procedure in $\procedures{T}$ \\
\midrule

$s = e;$ & shared write, where $s \in \sharedvars$ and $e$ is an expression over $\variables{T}$ \\
\midrule

$x = s;$ & shared read,  where $x \in \variables{T}$ and $s \in \sharedvars$ \\
\midrule

$\mutexlock{m};$   & mutex lock, where $m \in \mutexes$ \\
\midrule

$\mutexunlock{m};$ & mutex unlock, where $m \in \mutexes$\\
\bottomrule
\end{tabular}
\caption{Forms of statements in our simple programming model}\label{fig:statements}
\end{figure}

@@

\begin{figure}
\begin{tabular}{ll}
\textbf{Original Statement} & \textbf{Instrumented Statement} \\
\toprule

$s = e;$ & $\hasbeenwritten{i} = \hasbeenwritten{i} \cup \{ s \};$ \\
         & $\lockset{s}{i} = \lockset{s}{i} \cap \currentlockset{i};$ \\
\midrule

$x = s;$ & $\hasbeenread{i} = \hasbeenread{i} \cup \{ s \};$ \\
         & $\lockset{s}{i} = \lockset{s}{i} \cap \currentlockset{i};$ \\
         & $\havoc{\instrument{x}{i}};$ \\
\midrule

$\mutexlock{m};$   & $\currentlockset{i} = \currentlockset{i} \cup \{ m \};$ \\
\midrule

$\mutexunlock{m};$ & $\currentlockset{i} = \currentlockset{i} \setminus \{ m \};$ \\
\bottomrule
\end{tabular}
\caption{Instrumenting statements for static lockset analysis}\label{fig:instrumentation}
\end{figure}
